paper2_resistance_mechanisms_mixtures

### 2016-07-04 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
add ref
tweak

## References
1. GPIRM
1. Curtis 
1. Mani GS. Evolution of resistance in the presence of two insecticides. Genetics 1985;109(4):761–83.
1. Birget 2015

@@

1. what plots might I want to show for starting frequency ?
1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? Is it because the exposure to one insecticide also effects the development of resistance in the other ?
1. In discussion and maybe elewhere address potential concern that the relationships shown here may not hold for all of paramter space.
1. re-read GPIRM
1. can I develop explanatory diagrams to describe the input parameters ?
1. mention generation time of 1 month
1. mention other potential effects e.g. differential exposure of M&F, sex linkage, ...

>>>>

## References
1. GPIRM
1. Curtis 
1. Mani GS. Evolution of resistance in the presence of two insecticides. Genetics 1985;109(4):761–83.
1. Birget 2015
1. Curtis et al 1993, potential IRM strategies :
~ moderation : preserve susceptible genes by limiting selection pressure
~ saturation : high dose so that heterozygous resistants are killed
~ multiple attack : independently acting pressures neither of which is strong enough to lead to resistance

@@

1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? Is it because the exposure to one insecticide also effects the development of resistance in the other ?
1. In discussion and maybe elewhere address potential concern that the relationships shown here may not hold for all of paramter space.
1. re-read GPIRM
1. can I develop explanatory diagrams to describe the input parameters ?
1. mention generation time of 1 month
1. mention other potential effects e.g. differential exposure of M&F, sex linkage, ...
